\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-28 paper.tex
version 0.4 change to ACM format

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{ntheorem}
\usepackage{enumerate}
\usepackage[bottom]{footmisc}
\usepackage{soul}

%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
\soulregister\cite7
\soulregister\ref7
\pagestyle{plain}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\
}
\author{\IEEEauthorblockN{Huayi Jin$^1$}
}

@@

\begin{IEEEkeywords}
    Erasure Codes, Approximate Storage, Multimedia, Cloud Storage
\end{IEEEkeywords}

@@

@@

\subsection{Existing Erasure Codes}
RS/LRC/CLAY/SD/STAIR???

XOR-based

RS-based

RAID6

MSR

\subsection{Approximate Storage}
Approximate Storage loosen the requirement of storage reliability by allowing some quality loss of specific data, which recently receives more attentions since data centers are trading off the limited resource budget with the costly reliability requirements of ever-increasing data.

\subsection{Video Storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage. Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.

@@

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
Figure \ref{apcode-7222-v2} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.4\textwidth]{photo/apcode-7222-v2.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v2}
\end{figure}

@@

In \emph{phase 1}, we use RS$(h+s,h)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$. The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF). 
For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
As shown in the blod box in Figure \ref{apcode-7222-v2}, we use RS(5,3) in this phase.
\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
\end{equation}

In \emph{phase 2}, we use RS$(n,n-m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors. The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
As shown in orange chunks in Figure \ref{apcode-7222-v2}, we use RS(7,5) in this phase.

@@

@@

\bibliographystyle{IEEEtrans}
\bibliography{paper}

>>>>

%\documentclass[conference]{IEEEtran}
\documentclass[sigconf]{acmart}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{subfigure}
\usepackage{ntheorem}
\usepackage{enumerate}
\usepackage[bottom]{footmisc}
\usepackage{soul}

\usepackage{booktabs}

%\usepackage[T1]{fontenc}
%\usepackage{mathptmx}
%\soulregister\cite7
%\soulregister\ref7
%\pagestyle{plain}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\
}
\author{Huayi Jin$^1$}

@@

\begin{keywords}
    Erasure Codes, Approximate Storage, Multimedia, Cloud Storage
\end{keywords}

@@

\textcolor{red}
{Sixth paragraph:
Contribution of this paper, typically two or three contributions,
(1)	Propose a novel code Approximate Code
(2)	Give some mathematical proof to demonstrate the correctness of Approximate Code
(3)	Conduct several experiments to demonstrate the effectiveness of Approximate Code (no digitals here)}

\begin{table*}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & Computational Complexity \\ \hline
RS Code & any m disks & m disks & high & high & high \\ \hline
LRC Code & up to m disks & m global disks and r local disks & high & medium & medium \\ \hline
MSR Code & any m disks & m disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code & m disks and s sectors & m disks and s sectors & low & low & low \\ \hline
Approximate Code(Important) & m+s disks & m disks and s sectors & high & high & medium to high \\ \hline
Approximate Code(Ordinary) & m disks & m disks and s sectors & high & high & medium to high \\ \hline
\end{tabular}
\end{table*}

\textcolor{red}
{Seventh paragraph:
organization of the paper}

@@

\subsection{Existing Erasure Codes}

\textcolor{red}{Here we give some introduction to existing erasure codes
Specifically, we need to illustrate the existing erasure codes for video applications in detail.
Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}

\subsection{Video Storage}\label{video storage}
For normal HD (resolution 1280$\times$720, 8-bit, 30 fps) video, the amount of raw video data in 1 minute is 4.63 GB, so video data is usually encoded and compressed before storage. Lossy compression is a common method that provides a much lower compression ratio than lossless compression while ensuring tolerable loss of video quality, so we focus on such algorithms.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}

@@

\textcolor{red}{Something about H.264\dots}

\subsection{Approximate Storage}
Approximate Storage is another way outside of traditional methods of trading off the limited resource budget with the costly reliability requirements, which recently receives more attentions since data centers are faced with storage pressure from the ever-increasing data.

It loosens the requirement of storage reliability by allowing some quality loss of specific data. Therefore, programmers can specify the importance of the data segments and assign them to different storage blocks. The critical data is still safe because they are stored and redundantly backed up by expensive and highly reliable storage devices. Meanwhile, non-critical data is exposed to error, thus increasing storage density and saving cost.

However, it is too naive to store data in approximate storage units indiscriminately. Related research \cite{guo2016high} shows that this can lead to unacceptable data pollution. To ensure data quality in this case, higher error correction costs are required resulting in an increase in overall storage costs.

In the storage of video data, as described in \ref{video storage}, the I frame is the key to decoding the entire GOP. An error in the I frame will cause a decoding error in the P frames and the B frames, and the data loss of the I frame will cause the entire GOP to be undecodable. In contrast, the error or loss of a P frame has less impact, while the B frame is most tolerant of errors because no other frame depends on it.

@@

In the $n$ chunks of each stripe, $m$ ones are for coding and in the remaining $n-m$ chunks, we use $s \times t$ additional sectors for coding important data, where $s$ is the number of the columns and $t$ is the number of the rows.
Our design assumes that the parameters  $(n, m, s,t)$ are configurable parameters shus the constructor of the Approximate Code will be determined by these 4 parameters.
Although the choice of parameter $r$ is arbitrary, we recommend setting it to $r=s+h$.
The relevant instructions will be shown in \ref{Data Distribution}.
Meanwhile, we label $h=n-m-s$ as the number of columns of important data for convenience.
Figure \ref{apcode-7222-v5} shows an example of Approximate Codes with $n = 7$, $m = 2$, $s=2$ and $t = 2$, where we label the data disks with $d_{i,j}$, the important data parity sectors with $q_{i,j}$ and the normal parity sectors with $p_{i,j}$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{photo/apcode-7222-v5.PDF}
\caption{A sample of Approximate Codes $(7,2,2,2)$ with 7 chunks where 2 of them are parity chunks (presented by orange) and 4 other sectors (presented by red) are designed for encoding important data. In this example, there are 6 sectors (presented by dark blue) for important data and 15 sectors (presented by light blue) for normal data.}
\label{apcode-7222-v5}
\end{figure}

@@

In \emph{phase 1}, we use RS$(h+s,h)$ to encode $h$ groups of important data sectors and generate $s$ groups of parity sectors labeled with $q_{i,j}$. The calculation of $q_{i,j}$ are defined by equation \ref{q_ij}, where $\alpha_k$ is the coefficient in Galois Field (GF). 
For example, $q_{1,1} = \alpha_0^2 d_{1,0} + \alpha_1^2 d_{1,1} + \alpha_2^2 d_{1,2}$.
As shown in the blod box in Figure \ref{apcode-7222-v5}, we use RS(5,3) in this phase.
\begin{equation}\label{q_ij}
    q_{i,j} = \sum_{k=0}^{h-1} \alpha_k^{j+1} d_{i,k}
\end{equation}

In \emph{phase 2}, we use RS$(n,n-m)$ to generate $m$ parity chunks labeled with $p_{i,j}$ from $n-m$ chunks consist of data sectors and important parity sectors. The calculation of $p_{i,j}$ are defined by equation \ref{p_ij_1} and \ref{p_ij_2}.
Despite the difference in expression, the encoding process for $p_{i,j(i<t)}$ and $p_{i,j(i \geqslant t)}$ are same on chunk level because we treat $q_{i,j}$ and $b_{i,j}$ as the same on chunk level.
For example, $p_{1,1} = \alpha_0^4 d_{1,0} + \alpha_1^4 d_{1,1} + \alpha_2^4 d_{1,2} + \alpha_3^4 q_{1,0} + \alpha_4^4 q_{1,1}$.
As shown in orange chunks in Figure \ref{apcode-7222-v5}, we use RS(7,5) in this phase.

@@

\subsubsection{Decoding Process}
The decoding process can be partitioned into two modes: full recovery mode and approximate recovery mode. When no more than $m$ chunks lost, the system can fully recover

@@
